### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@699c8756b24d696b38e4476ceb811a802c5c49e5 🚀

\hypertarget{graph-embedding-offers-promises-the-inference-of-potential-interactions}{%
\section{Graph embedding offers promises the inference of potential
interactions}\label{graph-embedding-offers-promises-the-inference-of-potential-interactions}}

@@

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedded object & Reference\tabularnewline
\midrule
\endhead
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
\bottomrule
\end{longtable}

@@

>>>>

\hypertarget{graph-embedding-offers-promises-for-the-inference-of-potential-interactions}{%
\section{Graph embedding offers promises for the inference of potential
interactions}\label{graph-embedding-offers-promises-for-the-inference-of-potential-interactions}}

@@

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedded object & Reference\tabularnewline
\midrule
\endhead
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
SDNE & nodes through auto-encoding & Wang et al. (2016)\tabularnewline
\bottomrule
\end{longtable}

@@

\leavevmode\hypertarget{ref-Wang2016StrDee}{}%
Wang, D., Cui, P., \& Zhu, W. (2016). Structural Deep Network Embedding.
\emph{Proceedings of the 22nd ACM SIGKDD International Conference on
Knowledge Discovery and Data Mining}, 1225--1234.
\url{https://doi.org/10.1145/2939672.2939753}
